\documentclass[letterpaper,11pt]{article}


 \usepackage{setspace,array,
  amsmath,apjfonts,amsfonts,amssymb,enumerate,graphicx,
  longtable,float,times,textcomp,verbatim,url,nicefrac,
  currvita, tabularx, lipsum,enumitem,xcolor ,hyperref}

%page info
\setlength{\textwidth}{7.0in} 
\setlength{\textheight}{9.in}
\setlength{\topmargin}{-0.50in} 
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{0.25in} 

%get two columns
\newcolumntype{L}{>{\raggedright}p{0.15\textwidth}}
\newcolumntype{R}{p{0.81\textwidth}}

\newcolumntype{A}{ >{\raggedleft}p{0.03\textwidth}}
\newcolumntype{a}{p{0.70\textwidth}}
\newcolumntype{b}{ >{\raggedleft}p{0.21\textwidth}}


\newcolumntype{z}{p{1.0\textwidth}}
\newcommand\Tstrut{\rule{0pt}{2.6ex}}       % top strut
\newcommand\Bstrut{\rule[-1.1ex]{0pt}{0pt}} % bottom strut\

%counters
\newcounter{pubs}
\newcounter{invites}
\newcounter{confs}

%pub entry
\newcommand{\publication}[1]{ {\raggedright\stepcounter{pubs}\thepubs.\,\,#1\\}}

%contirubted talk
\newcommand{\talk}[2]{ \begin{tabular}{Aab}\stepcounter{confs}\theconfs.&#1&#2\end{tabular}}
\newcommand{\invite}[2]{ \begin{tabular}{Aab} \stepcounter{invites}\theinvites.  &#1&#2 \end{tabular}}
\newcommand{\award}[2]{#1\hfill#2}


\newcommand{\gradstudent}[3]{\begin{tabular}{
>{\raggedright}p{0.25\textwidth}
>{\raggedright}p{0.38\textwidth}
>{\raggedleft}p{0.1\textwidth}} #1&#2&#3\end{tabular} }
\newcommand{\student}[2]{#1\hfill #2}
%\newcommand{\talk}[2]{ \begin{tabular}{ab} #1 &#2 \end{tabular} }

%compact lists
\newlist{compactenum}{enumerate}{4}
\setlist[compactenum,1]{nolistsep,after=\vspace{\baselineskip},label=\arabic}
%compact lists
\newlist{compactitem}{itemize}{4}
\setlist[compactitem,1]{topsep=0pt,nolistsep,after=\vspace{\baselineskip}, label=\textbullet}

%journals
\newcommand{\apj}{\textit{Astrophysical Journal}}
\newcommand{\pasp}{\textit{Publications of the Astronomical Society of the Pacific}}
\newcommand{\mnras}{\textit{Monthly Notices of the Royal Astronomical Society}}

%make the links nice
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}


%header
%\pagestyle{myheadings}
%\markright{ STScI Postdoctoral \#16-0249 -- M. M. Fausnaugh}
%\pagenumbering{arabic}


\begin{document}

\begin{center}
\huge\bfseries{Michael M. Fausnaugh}
\end{center}

\noindent MIT Kavli Institute for Astrophysics and Space Research \hfill Office: (617) 324 6404 \\
77 Massachusetts Avenue, 37-535  \hfill faus@mit.edu\\
Cambridge, MA 02139 \hfill space.mit.edu/home/faus/
\\
\\
\underline{\textbf{Research Expertise}}\\
Time Domain Astronomy, Supermassive Black Holes, Astrophysical Transients
\\
\\
\underline{\textbf{Current Position}} \\
Reseach Scientist, \textbf{Massachusetts Institute of Technology,} Cambridge, MA \hfill 2017--present\\
Responsibilities: \begin{compactitem}
   \item Data Analysis and Quality Assurance for NASA's TESS mission
   \item Mission and Observation Planning for TESS
   \item Original Research Programs
   \end{compactitem}	
%%   \\
%%
%%  &\textbf{The Ohio State University,} Columbus, OH\\
%%  2016--2017 & OSU Presidential Fellow\\
%%  2013--2016 & Graduate Research Assistant \\
%%  2012--2013 & Graduate Teaching Assistant \\
%%  &\textbf{Adler Planetarium,} Chicago, OH\\
%%  2011--2012 & Research Assistant, VERITAS Telescope Array\\
%%  &  ARIEL Internship, awarded and funded by St. John's College \\
  %%  \\
\underline{\textbf{Education}}    \\
Ph.D., Astronomy, The Ohio State University;  Advisor:  Prof. Bradley Peterson \hfill 2017\\
M.S.,  \,\,Astronomy, The Ohio State University \hfill 2014\\
B.A., \,\,History of Math and Science, Philosophy, St. John's College, Santa Fe, NM\hfill 2011\\
\\
\noindent\underline{\textbf{Professional Experience}}\\ 
 Five \textbf{first author} papers accepted (147 citations). \\
 68 \textbf{papers} total,  15 minor publications.\\ %minor includes AAS abstracts, RNAAS, ATels, GCNs
% & 12 \textbf{professional presentations} including 1 invited seminar.\\
 Data Release Notes for NASA's TESS mission, \textbf{lead author}.\hfill 2018--present\\
\textbf{Referee} for \textit{Nature}, leading astrophysics journals (\textit{Nature Astronomy}, \textit{ApJ},\\ 
\indent \textit{MNRAS}, \textit{Astronomy \& Astrophysics}, \textit{PASP}), and
   general journal \textit{Frontiers}.\hfill 2016--present\\% in Astronomy and Space Science}.  \\
 \textbf{Chair and Organizer} for the special session "TESS and Transient Science" at  AAS 235. \hfill Jan 2020\\
  \textbf{Co-Chair} of LOC for the New England Regional Quasar and AGN Meeting\hfill May 2019\\
   \textbf{Mentor} for 2 graduate students and 3 undergraduates.\hfill 2017--present\\
\\
\noindent\underline{\textbf{Honors and Awards}}\\
\award{NASA Silver Achievement Award for the TESS Mission}{Sept 2019}\\
\award{OSU Hayes Research Forum, 2nd place Oral Presentation}{March 2017} \\
\award{OSU Markowitz Award for Excellence in Observational Astronomy}{2016--2017}\\
\award{OSU Graduate School Presidential Fellow}{2016--2017}\\
\award{St. John's College Award for Sustained Academic Excellence}{May 2011}\\
\award{St. John's College ARIEL Internship}{May 2011}\\
\\
%%\underline{\smash{\textbf{Research/}}}\\\underline{\smash{\textbf{Skills}}}&
%%%latex and html?
%%\begin{tabular}[t]{lll}
%%\textbf{Interests}         &  \textbf{Experience}               &\textbf{Programming} \\
%%Super-massive black holes  &  Data reduction, analysis,         &  Adept in python    \\
%%Extra-galactic astronomy   &  \phantom{a}\& visualization       &  Proficient in matlab, \\
%%Observational astronomy    &  Image processing                  &  \phantom{a}bash, latex, git  \\
%%Data analysis methods      &  Time series analysis              &  Working knowledge \\         
%%                           &  Software design, implementation,  &  \phantom{aa}of c++, fortran, perl \\
%%                           &    \phantom{a} and management      &                                  
%%\end{tabular}\\
%\begin{longtable}{z}
%\underline{\smash{\textbf{Invited Seminars}}}&  \\
%\begin{enumerate}[noitemsep,label=\arabic*.]
%\begin{enumerate}
%\item dadada
%verbose version
%\item 2019 April 18, "One Year for TESS:  The Science, Early Findings, and Future Ahead". \\
%Lunch and Learn Seminar, Northrop Grumman Innovation Systems, Sterling, VA.
%\item 2016 November 29,``Reverberation Mapping of AGN Accretion Disks'".\\
 %Galaxy and Cosmology Seminar, Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics. Cambridge, Massachusetts.
%\end{enumerate}
\noindent\underline{\textbf{Presentations}}\\
\textbf{Invited Talks}\\
\talk{AAS 235 Special Session "TESS and Transient Science." Honolulu, HI.}{Jan 2020}\\
\talk{"One Year for TESS:  Early Findings and the Future Ahead."  Northrop Grumman Innovation Systems, Sterling, VA.}{April 2019}\\
\talk{CCAP Summer Seminar, The Ohio State University. Columbus, OH.}{June 2016}\\
\talk{Galaxy and Cosmology Seminar.  Harvard-Smithsonian Center for Astrophysics. Cambridge, MA.}{Nov 2016}\\
\\
\textbf{TESS Contributed Research}\\
\talk{TESS Science Conference.  MIT.  Cambridge, MA.}{Aug 2019}\\
\talk{Meeting of the American Astronomical Society \#233. Seattle, WA.}{Jan 2019}\\
\talk{TESS Science Meeting. MIT. Cambridge, MA.}{Oct. 2018}\\
\textbf{AGN Contributed Research}\\
\talk{NERQUAM 2019.  MIT. Cambridge, MA.}{May 2019}\\
\talk{AGN STORM Research Meeting.  Atlanta, GA.}{Aug 2017}\\
\talk{Hayes Research Forum. The Ohio State University. Columbus, OH.}{March 2017}\\
\talk{AGN Research Group Meeting.  Space Telescope and Science Institute. Baltimore, MD.}{Feb 2017}\\
\talk{MIT Kavli Institute Research Lunch. Cambridge, MA.}{Jan 2017}\\
\talk{Meeting of the American Astronomical Society \#229. Grapevine, TX.}{Jan 2017}\\
\talk{AGN STORM Workshop. Reykjavik, Iceland.}{July 2016}\\
\talk{Great Lakes Quasar Symposium, Western University. London, Ontario.}{May 2016}\\
\talk{Narayan Research Group, Harvard-Smithsonian Center for Astrophysics. Cambridge, MA.}{April 2016}\\
\talk{Quasar Research Group Meeting,  Harvard-Smithsonian Center for Astrophysics. Cambridge, MA.}{April 2016}\\
\talk{AGN Research Group Meeting.  Space Telescope and Science Institute. Baltimore, MD.}{March 2016}\\
\talk{AGN STORM Workshop.  Columbus, OH.}{July 2015}\\
\talk{Meeting of the American Astronomical Society \#225. Seattle, WA.}{Jan 2015}\\
\talk{AGN Research Retreat.  University of St. Andrews.  St. Andrews, Scotland.}{Jan 2015}\\
\talk{Catolica Workshop.  The Ohio State University. Columbus, OH.}{May 2014}\\
\talk{Spitz Summer Institute, planetarium workshop/training. Spitz Inc. Chadds Ford, PA.}{July 2013}\\
\\
%verbose verseion
%\begin{enumerate}[noitemsep,label=\arabic*.]
%\item \talk{2017 March 3: Hayes Research Forum. The Ohio State University. Columbus, OH.}
%\item \talk{2017 February 27: AGN Research Group Meeting.  Space Telescope and Science Institute. Baltimore, MD.}
%\item \talk{2017 January 11: MIT Kavli Institute Research Lunch. Cambridge, MA.}
%\item \talk{2017 January 7: Meeting of the American Astronomical Society \#229. Grapevine, TX.}
%\item \stepcounter{confs}\theconfs.\,\,2016 July. AGN STORM Workshop. Reykjavik, Iceland.
%\item \talk{2016 June 21: Center for Cosmology and Astroparticle Physics Seminar Series, The Ohio State University. Columbus, OH.}
%\item \talk{2016 May 2: Great Lakes Quasar Symposium, Western University. London, Ontario.}
%\item \talk{2016 April 11: R. Narayan's Research Group Meeting, Harvard-Smithsonian Center for Astrophysics. Cambridge, MA.}
%\item \talk{2016 April 1: Quasar Research Group Meeting,  Harvard-Smithsonian Center for Astrophysics. Cambridge, MA.}
%\item \talk{2016 March 25: AGN Research Group Meeting.  Space Telescope and Science Institute. Baltimore, MD.}
%\item \talk{2015 July: AGN STORM Workshop.  Columbus, OH.}
%\item \talk{2015 January: Meeting of the American Astronomical Society \#225. Seattle, WA.}
%\item \stepcounter{confs}\theconfs.\,\,2014 July:  AGN Research Retreat.  University of St. Andrews.  St. Andrews, Scotland.
%\item \talk{2014 May: Catolica Workshop.  The Ohio State University. Columbus, OH.}
%\item \stepcounter{confs}\theconfs.\,\,2013 July:  Spitz Summer Institute, planetarium workshop/training. Spitz Inc. Chadds Ford, PA.\\
\underline{\textbf{Mentoring and Teaching}}\\
\textbf{Mentor} for MIT Graduate Students:\hfill2019--present\\
\indent Guided dissertations, outlined and managed research projects.
\begin{itemize}[nosep,label=\textbullet]
\item Akshata Krishnamurthy (2019), Rahul Jayaraman (2019--present)
\end{itemize}
\textbf{Supervisor} through MIT Undergraduate Research Opportunity Program:\hfill2017--present\\
\indent Designed and managed research/programming projects, introduced students to \\
\indent best research practices.
\begin{itemize}[nosep,label=\textbullet]
\item Nadia Dimitrova (2017), Ally Hong (2018--present), Jason Yang (2019--present)
\end{itemize}\textbf{Graduate Teaching Associate}, The Ohio State University:\hfill2012--2013\\
\indent Graded exams, designed and lead review sessions.
\begin{itemize}[nosep, label=\textbullet]
\item Astro 2291,  Intro to Astronomy and Planets (calculus-based, Autumn 2012)
\item Astro 1161,  Intro to Astronomy and the Solar System (Spring 2013)
\end{itemize}
\textbf{Head Laboratory Assistant}, St. John's College:\hfill2010--2011\\
\indent Supervised and demonstrated classroom practica, developed and documented\\
 \indent  pedagogical experiments.\\
%\begin{itemize}[nosep,label=\textbullet]
%\item St. John's College Senior-year Laboratory \hfill 
%\end{itemize}
\textbf{Laboratory Assistant}, St. John's College:\hfill2009--2010\\
\indent Supervised and demonstrated classroom practica.\\
%\begin{itemize}[nosep,after=\vspace{\baselineskip},label=\textbullet]
%\item St. John's College Junior-year Laboratory\hfill 
%\end{itemize}
\clearpage
\noindent \underline{\textbf{Observing Experience}}\\
\textbf{Space-based}\\
Transiting Exoplanet Survey Satellite\\
\indent Monthly mission planning (2018--present):
\begin{itemize}[nosep,label=\textbullet]
\item Selected 20,000 targets for transiting planet search
\item Selected 1,900 guide stars
\item Performed quality checks, diagnostics, and engineering validation
\item Assessed and reported guiding performance and pointing stability
\end{itemize}
\textbf{Ground-based}\\
\begin{tabular}[t]{lrl}
Total:&                                        119 nights& (81 queue, 38 classical)\\
Large Binocular Telescope:&       54 nights& 2013-2016\\
MDM 2.4m Hiltner:&                   24 nights& 2012-2015\\
MDM 1.3m McGraw: &               18 nights& 2013-2014\\
CTIO SMARTS 1.3m: &              16 nights& 2015\\
VERITAS ($\gamma$-ray observatory): &   7 nights& 2011   \\ 
\end{tabular}
\\
\\


\noindent\underline{\textbf{Selected Outreach}}\\
Upper Arlington Library Summer Astronomy Series \hfill June 2014, 2015, 2016\\
Presented 2-4 planetarium shows per month. \hfill 2013-2016\\
\textbf{OSU Planetarium:} Wrote the following shows:\hfill2013--2015
\begin{itemize}[nosep,label=\textbullet]
\item \textit{OSU Planetarium Grand Reopening, The Sky Tonight.}
\item \textit{Journey through the Solar System.}
\item \textit{The Autumn Sky:  Hidden Treasures.}
\end{itemize}
%verbose version
%Wickliffe Elementary Space Day (2013 January 18).\\
%Bailey Elementary Astronomy mini-course (2013 March 15).\\
%4-H Science Saturday (2013 April 6).\\
%Blendon Middle School Career Day (2013 May 14).\\
%Hosted a high school student for 1 day (2014 May 28).\\
%Upper Arlington Library Summer Astronomy Series (June 2014, 2015, 2016).\\
\noindent Hosted a high school student for 1 day \hfill May 2014\\
Blendon Middle School Career Day \hfill  May 2013\\
4-H Science Saturday \hfill April 2013\\
Bailey Elementary Astronomy mini-course \hfill March 2013\\
Wickliffe Elementary Space Day \hfill  Jan 2013\\

\begin{center}
\huge\textbf{Publications}
\end{center}


%\vspace{2em}
%{\raggedright
%\lipsum[100]}
%
%\vspace{2em}
%\lipsum[100]

\begin{longtable}{LR}

\underline{\smash{\textbf{First Author}}}
&%{\raggedright(\stepcounter{pubs}\thepubs. Distributed to co-authors for comments 2016~Oct.~17)\\
%``Continuum Reverberation Mapping of the Accretion Disks in Two \\Seyfert 1  Galaxies''\\
%\textbf{M.~M.~Fausnaugh} et al. (71 authors)\\
%Preprint available:  www.astronomy.ohio-state.edu/\textasciitilde fausnaugh/RMdisks\\}
\publication{``Continuum Reverberation Mapping of the Accretion Disk in Two \\Seyfert 1  Galaxies''\\
\textbf{M.~M.~Fausnaugh} et al. (71 authors), \apj, 854:107 (2018).  }
\\
&\publication{``Reverberation Mapping of Optical Emission Lines in Five Active Galaxies''\\
\textbf{M.~M.~Fausnaugh} et al. (71 authors), \apj, 840:97 (2017).}
\\
&\publication{``A New Approach to the Internal Calibration of Reverberation \\Mapping Spectra''\\
\textbf{M.~M.~Fausnaugh} (single author), \pasp, 129:972 (2017).  Includes first video abstract ever published by PASP.}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping Project. III. Optical Continuum Emission and Broad-Band Time Delays in NGC 5548''\\
\textbf{M.~M.~Fausnaugh} et al. (99 authors), \apj, 821:56 (2016).}
\\
& \publication{``The Cepheid distance to the maser-host galaxy NGC 4258: studying systematics with the Large Binocular Telescope''\\
\textbf{M.~M.~Fausnaugh}, C.~S.~Kochanek,  J.~R.~Gerke, L.~M.~Macri, A.~G.~Riess, K.~Z.~Stanek, \mnras, 450:3597 (2015).}
\\




\underline{\smash{\textbf{Major}}}\\\underline{\smash{\textbf{Contributing}}}\\\underline{\smash{\textbf{Author}}}
&\publication{``Space Telescope and Optical Reverberation Mapping Project. V. Optical Spectroscopic Campaign and Emission-Line Analysis for NGC 5548'',
  L.~Pei, \textbf{M.~M.~Fausnaugh}, and 152 others, \apj, 837:131 (2017).}
\\
&\publication{``Swift Monitoring of NGC 4151: Evidence for a Second X-ray/UV Reprocessing'',
R.~Edelson, J.~Gelbord, E.~Cackett, C.~Done, \textbf{M.~M.~Fausnaugh}, and 37 others \apj, 840:41 (2017).}
\\
&\publication{``Spitzer Space Telescope Measurements of Dust Reverberation Lags in the Seyfert 1 Galaxy NGC 6418'', 
  B.~Vazquez, P.~Galianni, M.~Richmond, A.~Robinson, D.~J.~Axon, K.~Horne, T.~Almeyda, \textbf{M.~M.~Fausnaugh}, and 18 others, \apj, 801:127 (2015).}
\\


\underline{\smash{\textbf{Contributing}}}\\\underline{\smash{\textbf{Author}}}
&\publication{``Space Telescope and Optical Reverberation Mapping
  Project. VII. Understanding the Ultraviolet Anomaly in NGC 5548 with
  X-Ray Spectroscopy'', Mathur,~S. et al. (150 authors, including
  \textbf{M.~M.~Fausnaugh}) \apj, 846:55 (2017).}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping
  Project. VI. Reverberating Disk Models for NGC\,5548'', D.~Starkey,
  K.~Horne, \textbf{M.~M.~Fausnaugh}, and 96 others, \apj, 835:65
  (2017).}  \\ &\publication{``Space Telescope and Optical
  Reverberation Mapping Project. IV. Anomalous behavior of the broad
  ultraviolet emission lines in NGC 5548'', M.~R.~Goad et al. (102
  authors, including \textbf{M.~M.~Fausnaugh}), \apj, 824:11 (2016).}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping
  Project. II. Swift and HST Reverberation Mapping of the Accretion
  Disk of NGC 5548'', R.~Edelson et al. (50 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 806:129 (2015).}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping
  Project. I. Ultraviolet Observations of the Seyfert 1 Galaxy NGC
  5548 with the Cosmic Origins Spectrograph on Hubble Space
  Telescope'', G.~ De~Rosa et al. (50 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 806:128 (2015).}
\\
&
\publication{``Swift/UVOT Grism Monitoring of NGC 5548
  in 2013: An Attempt at MgII Reverberation Mapping'', E.~M.~Cackett,
  K.~G\"ultekin, M.~C.~Bentz, \textbf{M.~M.~Fausnaugh},
  B.~M.~Peterson, J.~Troyer, M.~Vestergaard, \apj, 810:86 (2015).}
\\
&\publication{``XMM-Newton Observations of the Peculiar Cataclysmic
  Variable Lanning 386: X-ray evidence for a Magnetic Primary'',
  M.~R.~Kennedy, P.~Callanan, P.~M.~Garnavich,
  \textbf{M.~M.~Fausnaugh}, J.~C.~Zinn, \mnras, 466:2202
  (2017).}\\ &\publication{``Ground-based Parallax Confirmed by
  Spitzer: Binary Microlensing Event MOA-2015-BLG-020'', T.~Wang, et
  al. (87 authors, including \textbf{M.~M.~Fausnaugh}, \apj,
  845:129(2017).}
\\
&\publication{``OGLE-2015-BLG-1482L: The First Isolated Low-mass
  Microlens in the Galactic Bulge'', S.~J.~Chung (42 authors,
  including \textbf{M.~M.~Fausnaugh}), \apj, 838:154 (2017).}
\\
&\publication{``Toward a  Galactic Distribution
  of Planets. I. Methodology \& Planet Sensitivities of the 2015
  High-Cadence Spitzer Microlens Sample'', W.~Zhu et al. (28 authors,
  including \textbf{M.~M.~Fausnaugh}), submitted to \apj\ 2017 January
  18. }
\\
&\publication{``OGLE-2015-BLG-0196: Ground-based
  Gravitational Microlens Parallax Confirmed by Space-based
  Observation'', C.~Han et al. (26 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 834:82 (2017).}
\\
&\publication{``First simultaneous microlensing observations by two
  space telescopes: Spitzer \& Swift reveal a brown dwarf in event
  OGLE-2016-BLG-1319'', Y.~Shvartzvald et al. (94 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 831:183 (2016).}
\\
&\publication{``OGLE-2015-BLG-0479LA,B: Binary Gravitational
  Microlens Characterized by Simultaneous Ground-based and Space-based
  Observations'', C.~Han et al. (63 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 828:53 (2016).}
\\
&\publication{``The Spitzer Microlensing Program as a Probe for
  Globular Cluster Planets: Analysis of OGLE-2015-BLG-0448'',
  P.~Radoslaw et al. (92 authors, including \textbf{M.~M.~Fausnaugh}),
  \apj, 823:63 (2016).}
\\
&\publication{``Spitzer Observations of
  OGLE-2015-BLG-1212 Reveal a New Path to Breaking Strong Microlens
  Degeneracies'', V.~Bozza et al. (92 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 820:79 (2016).}
\\
&\publication{``Spitzer Microlens Measurement of a Massive Remnant
  in a Well-Separated Binary'', Y.~ Shvartzvald et al. (66 authors,
  including \textbf{M.~M.~Fausnaugh}), \apj, 814:111 (2015).}
\\
&\publication{``Spitzer IRAC Photometry for Time Series in Crowded
  Fields'', S.~ Calchi~ Novati et al. (25 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 814:92 (2015).}
\\
&\publication{``The Typecasting of Active Galactic Nuclei: Mrk 590
  no Longer Fits the Role'', K.~D.~Denney et al. (12 authors,
  including \textbf{M.~M.~Fausnaugh}), \apj, 796:134 (2014).}
\\
&\publication{``SN 2012au: A Golden Link between Superluminous
  Supernovae and Their Lower-luminosity Counterparts'',
  D.~Milisavlejic et al. (29 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 770:L38 (2013).}  \\


\underline{\smash{\textbf{Minor}}}\\\underline{\smash{\textbf{Publications}}}& \stepcounter{pubs}\thepubs--\addtocounter{pubs}{6}\thepubs.\,\,Seven \textit{Astronomer's Telegrams} with the ASAS-SN research group (\#5102, \#5110, \#6143, \#6158, \#8352, \#8356, \#9146, unrefereed, 2013--2016).\\
\\
&\publication{``TESS Data Processing and Quick-look Pipeline'', \textbf{M.~M.~Fausnaugh}; Xu Huang; Ana Glidden; Natalia Guerrero; TESS Science Office, Meeting of the American Astronomical Society \#231 (2018).}
\\
&\publication{``Reverberation Mapping of AGN Accretion Disks'',  
\textbf{M.~M.~Fausnaugh}, Meeting of the American Astronomical Society \#229 (2017).}
\\
&\publication{``AGN Space Telescope and Optical Reverberation Mapping Project II. Ultraviolet and Optical Continuum Analysis'',  
\textbf{M.~M.~Fausnaugh}, Meeting of the American Astronomical Society \#225 (2015).}
\\

\end{longtable}



\end{document}
