\documentclass[letterpaper,12pt]{article}


 \usepackage{setspace,array,
  amsmath,apjfonts,amsfonts,amssymb,enumerate,graphicx,
  longtable,float,times,textcomp,verbatim,url,nicefrac,
  currvita, tabularx, lipsum,enumitem, paralist,xcolor ,hyperref}

%page info
\setlength{\textwidth}{6.5in} 
\setlength{\textheight}{9.0in}
\setlength{\topmargin}{-0.5in} 
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in} 

%get two columns
\newcolumntype{L}{>{\raggedright}p{0.145\textwidth}}
\newcolumntype{R}{p{0.855\textwidth}}

%counters
\newcounter{pubs}
\newcounter{invites}
\newcounter{confs}

%pub entry
\newcommand{\publication}[1]{ {\raggedright\stepcounter{pubs}\thepubs.\,\,#1\\}}

%contirubted talk
\newcommand{\talk}[1]{ {\raggedright\stepcounter{confs}\theconfs.\,\,\textbf{Contributed talk.}\,\,#1}}

%journals
\newcommand{\apj}{\textit{Astrophysical Journal}}
\newcommand{\pasp}{\textit{Publications of the Astronomical Society of the Pacific}}
\newcommand{\mnras}{\textit{Monthly Notices of the Royal Astronomical Society}}

%make the links nice
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}


%header
%\pagestyle{myheadings}
%\markright{ CV -- M. M. Fausnaugh}
%\pagenumbering{arabic}


\begin{document}

\begin{center}
\huge\textbf{Publications}
\end{center}


%\vspace{2em}
%{\raggedright
%\lipsum[100]}
%
%\vspace{2em}
%\lipsum[100]

\begin{longtable}{LR}

\underline{\smash{\textbf{First Author}}}
&{\raggedright(\stepcounter{pubs}\thepubs. Distributed to co-authors for final comments 2016~Oct.~17)\\
``Continuum Reverberation Mapping of the Accretion Disks in Two \\Seyfert 1  Galaxies''\\
\textbf{M.~M.~Fausnaugh} et al. (71 authors)\\
Preprint available:  www.astronomy.ohio-state.edu/\textasciitilde fausnaugh/RMdisks\\}
%\publication{``Continuum Reverberation Mapping of the Accretion Disk in Two Seyfert 1  Galaxies''\\
%\textbf{M.~M.~Fausnaugh} et al. (71 authors), in prep, distributed to co-authors for final comments 2016 Oct.~28.  Private preprint:  www.astronomy.ohio-state.edu/\textasciitilde fausnaugh/RMdisks}
\\
&\publication{``Reverberation Mapping of Optical Emission Lines in Five Active Galaxies''\\
\textbf{M.~M.~Fausnaugh} et al. (71 authors), submitted to \apj\ 2016~Oct.~1, arXiv:1610.00008 (2016).}
\\
&\publication{``A New Approach to the Internal Calibration of Reverberation Mapping Spectra''\\
\textbf{M.~M.~Fausnaugh} (single author), accepted to \pasp\ 2016~Oct.~11, arXiv:1609.04014 (2016).}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping Project. III. Optical Continuum Emission and Broad-Band Time Delays in NGC 5548''\\
\textbf{M.~M.~Fausnaugh} et al. (99 authors), \apj, 821:56 (2016).}
\\
& \publication{``The Cepheid distance to the maser-host galaxy NGC 4258: studying systematics with the Large Binocular Telescope''\\
\textbf{M.~M.~Fausnaugh}, C.~S.~Kochanek,  J.~R.~Gerke, L.~M.~Macri, A.~G.~Riess, K.~Z.~Stanek, \mnras, 450:3597 (2015).}
\\




\underline{\smash{\textbf{Major}}}\\\underline{\smash{\textbf{Contributing}}}\\\underline{\smash{\textbf{Author}}}
&\publication{``Space Telescope and Optical Reverberation Mapping Project. V. Optical Spectroscopic Campaign and Emission-Line Analysis for NGC 5548'',
  L.~Pei, \textbf{M.~M.~Fausnaugh}, and 152 others, submitted to \apj\ 2016~Oct.~21.}
\\
&\publication{``Swift Monitoring of NGC 4151: Evidence for a Second X-ray/UV Reprocessing'',
R.~Edelson, J.~Gelbord, E.~Cackett, C.~Done, \textbf{M.~M.~Fausnaugh}, and 37 others, submitted to \apj\ 2016~Oct.~20.}
\\
&\publication{``Spitzer Space Telescope Measurements of Dust Reverberation Lags in the Seyfert 1 Galaxy NGC 6418'', 
  B.~Vazquez, P.~Galianni, M.~Richmond, A.~Robinson, D.~J.~Axon, K.~Horne, T.~Almeyda, \textbf{M.~M.~Fausnaugh}, and 18 others, \apj, 801:127 (2015).}
\\


\underline{\smash{\textbf{Contributing}}}\\\underline{\smash{\textbf{Author}}}
&\publication{``Space Telescope and Optical Reverberation Mapping Project. VI. Reverberating Disk Models for NGC\,5548'',
  D.~Starkey, K.~Horne, \textbf{M.~M.~Fausnaugh}, and 96 others, submitted to \apj\ 2016~Sept.~30.}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping Project. IV. Anomalous behavior of the broad ultraviolet emission lines in NGC 5548'', 
M.~R.~Goad et al. (102 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 824:11 (2016).}
\\
&\publication{``Space Telescope and Optical Reverberation Mapping Project. II. Swift and HST Reverberation Mapping of the Accretion Disk of NGC 5548'',
R.~Edelson et al. (50 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 806:129 (2015).}
\\    
&\publication{``Space Telescope and Optical Reverberation Mapping Project. I. Ultraviolet Observations of the  Seyfert 1 Galaxy NGC 5548 with the Cosmic Origins Spectrograph on Hubble Space Telescope'',
G.~ De~Rosa et al. (50 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 806:128 (2015).}
\\
&\publication{``Swift/UVOT Grism Monitoring of NGC 5548 in 2013: An Attempt at MgII 
  Reverberation Mapping'',  E.~M.~Cackett, K.~G\"ultekin, M.~C.~Bentz, \textbf{M.~M.~Fausnaugh}, B.~M.~Peterson, J.~Troyer, M.~Vestergaard, \apj, 810:86 (2015).}
\\
&\publication{``OGLE-2015-BLG-0479LA,B: Binary Gravitational Microlens Characterized by Simultaneous Ground-based and Space-based Observations'', 
C.~Han et al. (63 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 828:53 (2016).}
\\
&\publication{``First simultaneous microlensing observations by two space telescopes: Spitzer \& Swift reveal a brown dwarf in event OGLE-2016-BLG-1319'', 
Y.~Shvartzvald et al. (94 authors, including \textbf{M.~M.~Fausnaugh}, submitted to \apj), arXiv:1606.02292 (2016).}
\\
&\publication{``The Spitzer Microlensing Program as a Probe for Globular Cluster Planets:  Analysis of OGLE-2015-BLG-0448'', 
P.~Radoslaw et al. (92 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 823:63 (2016).}
\\
&\publication{``Spitzer Observations of OGLE-2015-BLG-1212 Reveal a New Path to Breaking Strong Microlens Degeneracies'',  
V.~Bozza et al. (92 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 820:79 (2016).}
\\
&\publication{``Spitzer Microlens Measurement of a Massive Remnant in a Well-Separated Binary'',
Y.~ Shvartzvald et al. (66 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 814:111 (2015).}
\\
&\publication{``Spitzer IRAC Photometry for Time Series in Crowded Fields'', 
S.~ Calchi~ Novati et al. (25 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 814:92 (2015).}
\\
&\publication{``The Typecasting of Active Galactic Nuclei: Mrk 590 no Longer Fits the Role'',
K.~D.~Denney et al. (12 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 796:134 (2014).}
\\
&\publication{``SN 2012au: A Golden Link between Superluminous Supernovae and Their Lower-luminosity Counterparts'',
D.~Milisavlejic et al. (29 authors, including \textbf{M.~M.~Fausnaugh}), \apj, 770:L38 (2013).}
\\


\underline{\smash{\textbf{Minor}}}\\\underline{\smash{\textbf{Publications}}}& \stepcounter{pubs}\thepubs--\addtocounter{pubs}{6}\thepubs.\,\,Seven \textit{Astronomer's Telegrams} with the ASAS-SN research group (\#5102, \#5110, \#6143, \#6158, \#8352, \#8356, \#9146, unrefereed, 2013--2016).\\
\\
&\publication{``AGN Space Telescope and Optical Reverberation Mapping Project II. Ultraviolet and Optical Continuum Analysis'',  
\textbf{M.~M.~Fausnaugh}, Meeting of the American Astronomical Society \#225 (2015).}
\\




\end{longtable}

\end{document}