
\begin{center}
\huge\textbf{Publications}
\end{center}


%\vspace{2em}
%{\raggedright
%\lipsum[100]}
%
%\vspace{2em}
%\lipsum[100]


\noindent\underline{\textbf{First Author}}\\
\publication{``Continuum Reverberation Mapping of the Accretion Disk in Two Seyfert 1  Galaxies''
\textbf{M.~M.~Fausnaugh} et al. (71 authors), \apj, 854:107 (2018).  }\\
\publication{``Reverberation Mapping of Optical Emission Lines in Five Active Galaxies''
\textbf{M.~M.~Fausnaugh} et al. (71 authors), \apj, 840:97 (2017).}\\
\publication{``A New Approach to the Internal Calibration of Reverberation Mapping Spectra''
\textbf{M.~M.~Fausnaugh} (single author), \pasp, 129:972 (2017).  Includes first video abstract ever published by PASP.}\\
\publication{``Space Telescope and Optical Reverberation Mapping Project. III. Optical Continuum Emission and Broad-Band Time Delays in NGC 5548''
\textbf{M.~M.~Fausnaugh} et al. (99 authors), \apj, 821:56 (2016).}\\
\publication{``The Cepheid distance to the maser-host galaxy NGC 4258: studying systematics with the Large Binocular Telescope''\textbf{M.~M.~Fausnaugh}, C.~S.~Kochanek,  J.~R.~Gerke, L.~M.~Macri, A.~G.~Riess, K.~Z.~Stanek, \mnras, 450:3597 (2015).}\\
\\
\noindent\underline{\textbf{Major Contributing Author}}\\
\publication{``Space Telescope and Optical Reverberation Mapping Project. V. Optical Spectroscopic Campaign and Emission-Line Analysis for NGC 5548'',
  L.~Pei, \textbf{M.~M.~Fausnaugh}, and 152 others, \apj, 837:131 (2017).}\\
\publication{``Swift Monitoring of NGC 4151: Evidence for a Second X-ray/UV Reprocessing'',
  R.~Edelson, J.~Gelbord, E.~Cackett, C.~Done, \textbf{M.~M.~Fausnaugh}, and 37 others \apj, 840:41 (2017).}\\
\publication{``Spitzer Space Telescope Measurements of Dust Reverberation Lags in the Seyfert 1 Galaxy NGC 6418'', 
  B.~Vazquez, P.~Galianni, M.~Richmond, A.~Robinson, D.~J.~Axon, K.~Horne, T.~Almeyda, \textbf{M.~M.~Fausnaugh}, and 18 others, \apj, 801:127 (2015).}\\
\\
\noindent\underline{\textbf{Contributing Author}}\\
\noindent\textbf{TESS: Exoplanets}

\noindent\textbf{TESS: Difference Imaging Analysis}


\noindent\textbf{AGN STORM}\\
\publication{``Space Telescope and Optical Reverberation Mapping
  Project. VII. Understanding the Ultraviolet Anomaly in NGC 5548 with
  X-Ray Spectroscopy'', Mathur,~S. et al. (150 authors, including
  \textbf{M.~M.~Fausnaugh}) \apj, 846:55 (2017).}\\
\publication{``Space Telescope and Optical Reverberation Mapping
  Project. VI. Reverberating Disk Models for NGC\,5548'', D.~Starkey,
  K.~Horne, \textbf{M.~M.~Fausnaugh}, and 96 others, \apj, 835:65
  (2017).}\\
\publication{``Space Telescope and Optical
  Reverberation Mapping Project. IV. Anomalous behavior of the broad
  ultraviolet emission lines in NGC 5548'', M.~R.~Goad et al. (102
  authors, including \textbf{M.~M.~Fausnaugh}), \apj, 824:11 (2016).}\\
\publication{``Space Telescope and Optical Reverberation Mapping
  Project. II. Swift and HST Reverberation Mapping of the Accretion
  Disk of NGC 5548'', R.~Edelson et al. (50 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 806:129 (2015).}\\
\publication{``Space Telescope and Optical Reverberation Mapping
  Project. I. Ultraviolet Observations of the Seyfert 1 Galaxy NGC
  5548 with the Cosmic Origins Spectrograph on Hubble Space
  Telescope'', G.~ De~Rosa et al. (50 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 806:128 (2015).}\\

\noindent\textbf{AGN Science}\\

\publication{"The first spectroscopic dust reverberation programme on
  active galactic nuclei: the torus in NGC 5548'', H.~Landt et al. (19 authors,
  including \textbf{M.~M.~Fausnaugh}), \mnras, 439:1572 (2019).}\\

\publication{``The Typecasting of Active Galactic Nuclei: Mrk 590
  no Longer Fits the Role'', K.~D.~Denney et al. (12 authors,
  including \textbf{M.~M.~Fausnaugh}), \apj, 796:134 (2014).}\\
\publication{``Swift/UVOT Grism Monitoring of NGC 5548
  in 2013: An Attempt at MgII Reverberation Mapping'', E.~M.~Cackett,
  K.~G\"ultekin, M.~C.~Bentz, \textbf{M.~M.~Fausnaugh},
  B.~M.~Peterson, J.~Troyer, M.~Vestergaard, \apj, 810:86 (2015).}\\

\noindent\textbf{Spitzer Microlensing Campaign}\\
\publication{``Ground-based Parallax Confirmed by
  Spitzer: Binary Microlensing Event MOA-2015-BLG-020'', T.~Wang, et
  al. (87 authors, including \textbf{M.~M.~Fausnaugh}, \apj,
  845:129(2017).}\\
\publication{``OGLE-2015-BLG-1482L: The First Isolated Low-mass
  Microlens in the Galactic Bulge'', S.~J.~Chung (42 authors,
  including \textbf{M.~M.~Fausnaugh}), \apj, 838:154 (2017).}\\
\publication{``Toward a  Galactic Distribution
  of Planets. I. Methodology \& Planet Sensitivities of the 2015
  High-Cadence Spitzer Microlens Sample'', W.~Zhu et al. (28 authors,
  including \textbf{M.~M.~Fausnaugh}), submitted to \apj\ 2017 January
  18. }\\
\publication{``OGLE-2015-BLG-0196: Ground-based
  Gravitational Microlens Parallax Confirmed by Space-based
  Observation'', C.~Han et al. (26 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 834:82 (2017).}\\
\publication{``First simultaneous microlensing observations by two
  space telescopes: Spitzer \& Swift reveal a brown dwarf in event
  OGLE-2016-BLG-1319'', Y.~Shvartzvald et al. (94 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 831:183 (2016).}\\
\publication{``OGLE-2015-BLG-0479LA,B: Binary Gravitational
  Microlens Characterized by Simultaneous Ground-based and Space-based
  Observations'', C.~Han et al. (63 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 828:53 (2016).}\\
\publication{``The Spitzer Microlensing Program as a Probe for
  Globular Cluster Planets: Analysis of OGLE-2015-BLG-0448'',
  P.~Radoslaw et al. (92 authors, including \textbf{M.~M.~Fausnaugh}),
  \apj, 823:63 (2016).}\\
\publication{``Spitzer Observations of
  OGLE-2015-BLG-1212 Reveal a New Path to Breaking Strong Microlens
  Degeneracies'', V.~Bozza et al. (92 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 820:79 (2016).}\\
\publication{``Spitzer Microlens Measurement of a Massive Remnant
  in a Well-Separated Binary'', Y.~ Shvartzvald et al. (66 authors,
  including \textbf{M.~M.~Fausnaugh}), \apj, 814:111 (2015).}\\
\publication{``Spitzer IRAC Photometry for Time Series in Crowded
  Fields'', S.~ Calchi~ Novati et al. (25 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 814:92 (2015).}\\

\noindent\textbf{Misc}\\
\publication{``SN 2012au: A Golden Link between Superluminous
  Supernovae and Their Lower-luminosity Counterparts'',
  D.~Milisavlejic et al. (29 authors, including
  \textbf{M.~M.~Fausnaugh}), \apj, 770:L38 (2013).}  \\
\publication{"SN 2012au: A Golden Link between Superluminous Supernovae and Their Lower-luminosity Counterparts", Dan~Milisavljevic et al. (28 authors, including M.~M.~Fausnaugh),\textit{ The Astrophysical Journal Letters }, 770:L38 (2013)  }\\
\publication{"SN 2012au: A Golden Link between Superluminous Supernovae and Their Lower-luminosity Counterparts", Dan~Milisavljevic et al. (28 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal Letters}, 770:L38 (2013).  }\\
\publication{"SN 2012au: A Golden Link between Superluminous Supernovae and Their Lower-luminosity Counterparts", Dan~Milisavljevic et al. (28 authors, including M.~M.~Fausnaugh), The Astrophysical Journal Letters, Volume 770, Issue 2, article id. L38, 6 pp. (2013).}\\

\publication{``XMM-Newton Observations of the Peculiar Cataclysmic
  Variable Lanning 386: X-ray evidence for a Magnetic Primary'',
  M.~R.~Kennedy, P.~Callanan, P.~M.~Garnavich,
  \textbf{M.~M.~Fausnaugh}, J.~C.~Zinn, \mnras, 466:2202
  (2017).}\\
\\

\noindent\underline{\textbf{Minor Publications}}\\
\stepcounter{pubs}\thepubs--\addtocounter{pubs}{6}\thepubs.\,\,Seven \textit{Astronomer's Telegrams} with the ASAS-SN research group (\#5102, \#5110, \#6143, \#6158, \#8352, \#8356, \#9146, unrefereed, 2013--2016).

\publication{``TESS Data Processing and Quick-look Pipeline'', \textbf{M.~M.~Fausnaugh}; Xu Huang; Ana Glidden; Natalia Guerrero; TESS Science Office, Meeting of the American Astronomical Society \#231 (2018).}

\publication{``Reverberation Mapping of AGN Accretion Disks'',  
\textbf{M.~M.~Fausnaugh}, Meeting of the American Astronomical Society \#229 (2017).}

\publication{``AGN Space Telescope and Optical Reverberation Mapping Project II. Ultraviolet and Optical Continuum Analysis'',  
\textbf{M.~M.~Fausnaugh}, Meeting of the American Astronomical Society \#225 (2015).}


