\begin{center}\huge\textbf{Publications}\end{center}

\noindent\underline{\textbf{First Author}}\\
\noindent\publication{"Continuum Reverberation Mapping of the Accretion Disks in Two Seyfert 1 Galaxies", M.~M.~Fausnaugh et al. (72 authors), \textit{The Astrophysical Journal}, 854:107 (2018).  }\\
\noindent\publication{"A New Approach to the Internal Calibration of Reverberation-Mapping Spectra", M.~M.~Fausnaugh, \textit{Publications of the Astronomical Society of the Pacific}, 129:024007 (2017).  }\\
\noindent\publication{"Reverberation Mapping of Optical Emission Lines in Five Active Galaxies", M.~M.~Fausnaugh et al. (71 authors), \textit{The Astrophysical Journal}, 840:97 (2017).  }\\
\noindent\publication{"Continuum Reverberation Mapping of AGN Accretion Disks", Michael~M.~Fausnaugh et al. (5 authors), \textit{Frontiers in Astronomy and Space Sciences}, 4:55 (2017).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. III. Optical Continuum Emission and Broadband Time Delays in NGC 5548", M.~M.~Fausnaugh et al. (97 authors), \textit{The Astrophysical Journal}, 821:56 (2016).  }\\
\noindent\publication{"The Cepheid distance to the maser-host galaxy NGC 4258: studying systematics with the Large Binocular Telescope", M.~M.~Fausnaugh et al. (6 authors), \textit{Monthly Notices of the Royal Astronomical Society}, 450:3597 (2015).  }\\
\\\\\noindent\underline{\textbf{Major Author}}\\
\textbf{Contributed major analysis or reduced data}\\
\noindent\publication{"An extreme amplitude, massive heartbeat system in the LMC characterized using ASAS-SN and TESS", T.~Jayasinghe et al. (6 authors, including M.~M.~Fausnaugh), \textit{Monthly Notices of the Royal Astronomical Society}, 489:4705 (2019).  }\\
\noindent\publication{"Velocity-resolved Reverberation Mapping of Five Bright Seyfert 1 Galaxies", G.~De Rosa et al. (102 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 866:133 (2018).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. V. Optical Spectroscopic Campaign and Emission-line Analysis for NGC 5548", L.~Pei et al. (156 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 837:131 (2017).  }\\
\noindent\publication{"Swift Monitoring of NGC 4151: Evidence for a Second X-Ray/UV Reprocessing", R.~Edelson et al. (44 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 840:41 (2017).  }\\
\noindent\publication{"Spitzer Space Telescope Measurements of Dust Reverberation Lags in the Seyfert 1 Galaxy NGC 6418", Billy~Vazquez et al. (25 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 801:127 (2015).  }\\
\\\\\noindent\underline{\textbf{Contributing Author}}\\
\noindent\textbf{TESS Exoplanets}\\
\textbf{Authorship acknowledges direct support of the TESS mission}\\
\noindent\publication{"Hot, rocky and warm, puffy super-Earths orbiting TOI-402 (HD 15337)", Xavier~Dumusque et al. (33 authors, including M.~M.~Fausnaugh), \textit{Astronomy \& Astrophysics}, 627:22 (2019).  }\\
\noindent\publication{"TESS Hunt for Young and Maturing Exoplanets (THYME): A Planet in the 45 Myr Tucana-Horologium Association", Elisabeth~R.~Newton et al. (52 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal Letters}, 880:L17 (2019).  }\\
\publication{"A super-Earth and two sub-Neptunes transiting the nearby and quiet M dwarf TOI-270", Maximilian~N.~G\"unther et al. (60 authors, including M.~M.~Fausnaugh),\textit{Nature Astronomy}, page 420 Jul 2019. }\\
\noindent\publication{"WASP-4b Arrived Early for the TESS  Mission", L.~G.~Bouma et al. (24 authors, including M.~M.~Fausnaugh), \textit{The Astronomical Journal}, 157:217 (2019).  }\\
\noindent\publication{"TESS Discovery of an Ultra-short-period Planet around the Nearby M Dwarf LHS 3844", Roland~Vanderspek et al. (73 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal Letters}, 871:L24 (2019).  }\\
\noindent\publication{"TESS Discovery of a Transiting Super-Earth in the pi Mensae System", Chelsea~X.~Huang et al. (66 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal Letters}, 868:L39 (2018).  }\\
\noindent\textbf{TESS: Difference Imaging Pipeline}\\
\textbf{Contributed analysis}\\
\noindent\publication{"Discovery and Early Evolution of ASASSN-19bt, the First TDE Detected by TESS", Thomas~W.~-S.~Holoien et al. (26 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 883:111 (2019).  }\\
\noindent\publication{"ASASSN-18tb: a most unusual Type Ia supernova observed by TESS and SALT", P.~J.~Vallely et al. (19 authors, including M.~M.~Fausnaugh), \textit{Monthly Notices of the Royal Astronomical Society}, 487:2372 (2019).  }\\
\noindent\textbf{AGN STORM}\\
\textbf{Co-I status}\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. X. Understanding the Absorption-line Holiday in NGC 5548", M.~Dehghanian et al. (30 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 877:119 (2019).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. VIII. Time Variability of Emission and Absorption in NGC 5548 Based on Modeling the Ultraviolet Spectrum", G.~A.~Kriss et al. (167 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 881:153 (2019).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. VII. Understanding the Ultraviolet Anomaly in NGC 5548 with X-Ray Spectroscopy", S.~Mathur et al. (150 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 846:55 (2017).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project.VI. Reverberating Disk Models for NGC 5548", D.~Starkey et al. (93 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 835:65 (2017).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. IV. Anomalous Behavior of the Broad Ultraviolet Emission Lines in NGC 5548", M.~R.~Goad et al. (101 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 824:11 (2016).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project. II. Swift and HST Reverberation Mapping of the Accretion Disk of NGC 5548", R.~Edelson et al. (50 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 806:129 (2015).  }\\
\noindent\publication{"Space Telescope and Optical Reverberation Mapping Project.I. Ultraviolet Observations of the Seyfert 1 Galaxy NGC 5548 with the Cosmic Origins Spectrograph on Hubble Space Telescope", G.~De Rosa et al. (50 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 806:128 (2015).  }\\
\noindent\textbf{AGN Misc}\\
\textbf{Co-I status}\\
\noindent\publication{"The first spectroscopic dust reverberation programme on active galactic nuclei: the torus in NGC 5548", H.~Landt et al. (19 authors, including M.~M.~Fausnaugh), \textit{Monthly Notices of the Royal Astronomical Society}, 489:1572 (2019).  }\\
\noindent\publication{"Anomalous behaviour of the UV-optical continuum bands in NGC 5548", M.~R.~Goad et al. (11 authors, including M.~M.~Fausnaugh), \textit{Monthly Notices of the Royal Astronomical Society}, 486:5362 (2019).  }\\
\noindent\publication{"The First Swift Intensive AGN Accretion Disk Reverberation Mapping Survey", R.~Edelson et al. (35 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 870:123 (2019).  }\\
\noindent\publication{"X-ray/UV/optical variability of NGC 4593 with Swift: reprocessing of X-rays by an extended reprocessor", I.~M.~McHardy et al. (28 authors, including M.~M.~Fausnaugh), \textit{Monthly Notices of the Royal Astronomical Society}, 480:2881 (2018).  }\\
\noindent\publication{"The Structure of the Broad-line Region in Active Galactic Nuclei. II. Dynamical Modeling of Data From the AGN10 Reverberation Mapping Campaign", C.~J.~Grier et al. (7 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 849:146 (2017).  }\\
\noindent\publication{"Swift/UVOT Grism Monitoring of NGC 5548 in 2013: An Attempt at MgII Reverberation Mapping", E.~M.~Cackett et al. (7 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 810:86 (2015).  }\\
\noindent\publication{"The Typecasting of Active Galactic Nuclei: Mrk 590 no Longer Fits the Role", K.~D.~Denney et al. (12 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 796:134 (2014).  }\\
\noindent\textbf{Spitzer Microlensing Campaign}\\
\textbf{Contributed observations}\\
\noindent\publication{"Ground-based Parallax Confirmed by Spitzer: Binary Microlensing Event MOA-2015-BLG-020", Tianshu~Wang et al. (91 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 845:129 (2017).  }\\
\noindent\publication{"OGLE-2015-BLG-1482L: The First Isolated Low-mass Microlens in the Galactic Bulge", S.~-J.~Chung et al. (42 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 838:154 (2017).  }\\
\noindent\publication{"Toward a Galactic Distribution of Planets. I. Methodology and Planet Sensitivities of the 2015 High-cadence Spitzer Microlens Sample", Wei~Zhu et al. (40 authors, including M.~M.~Fausnaugh), \textit{The Astronomical Journal}, 154:210 (2017).  }\\
\noindent\publication{"OGLE-2015-BLG-0196: Ground-based Gravitational Microlens Parallax Confirmed by Space-based Observation", C.~Han et al. (26 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 834:82 (2017).  }\\
\noindent\publication{"The First Simultaneous Microlensing Observations by Two Space Telescopes: Spitzer and Swift Reveal a Brown Dwarf in Event OGLE-2015-BLG-1319", Y.~Shvartzvald et al. (99 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 831:183 (2016).  }\\
\noindent\publication{"OGLE-2015-BLG-0479LA,B: Binary Gravitational Microlens Characterized by Simultaneous Ground-based and Space-based Observations", C.~Han et al. (68 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 828:53 (2016).  }\\
\noindent\publication{"The Spitzer Microlensing Program as a Probe for Globular Cluster Planets: Analysis of OGLE-2015-BLG-0448", Radosław~Poleski et al. (92 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 823:63 (2016).  }\\
\noindent\publication{"Spitzer Observations of OGLE-2015-BLG-1212 Reveal a New Path toward Breaking Strong Microlens Degeneracies", V.~Bozza et al. (108 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 820:79 (2016).  }\\
\noindent\publication{"Spitzer Microlens Measurement of a Massive Remnant in a Well-separated Binary", Y.~Shvartzvald et al. (73 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 814:111 (2015).  }\\
\noindent\publication{"Spitzer IRAC Photometry for Time Series in Crowded Fields", S.~Calchi Novati et al. (27 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal}, 814:92 (2015).  }\\
\noindent\textbf{Miscellaneous}\\
\textbf{Contributed observations}\\
\noindent\publication{"XMM-Newton observations of the peculiar cataclysmic variable Lanning 386: X-ray evidence for a magnetic primary", M.~R.~Kennedy et al. (5 authors, including M.~M.~Fausnaugh), \textit{Monthly Notices of the Royal Astronomical Society}, 466:2202 (2017).  }\\
\noindent\publication{"SN 2012au: A Golden Link between Superluminous Supernovae and Their Lower-luminosity Counterparts", Dan~Milisavljevic et al. (28 authors, including M.~M.~Fausnaugh), \textit{The Astrophysical Journal Letters}, 770:L38 (2013).  }\\
\\\\\noindent\underline{\textbf{Unrefereed Publications}}\\
\publication{"Big surprises from small supermassive black holes", Michael~Fausnaugh, \textit{Nature Astronomy}, page 694 Jun 2019. }\\
\publication{American Astronomical Society, AAS Meeting \#233, id.202.08, Jan 2019}\\
\noindent\publication{"A Simulated Data Set for the Transiting Exoplanet Survey Satellite", Jon~M.~Jenkins et al. (18 authors, including M.~M.~Fausnaugh), \textit{Research Notes of the American Astronomical Society}, 2:47 (2018).  }\\
\publication{American Astronomical Society, AAS Meeting \#231, id. 439.12, Jan 2018}\\
\publication{American Astronomical Society, AAS Meeting \#231, id. 439.09, Jan 2018}\\
\publication{American Astronomical Society, AAS Meeting \#231, id. 439.11, Jan 2018}\\
\publication{The Astronomer's Telegram, No. 9146, Jun 2016}\\
\publication{The Astronomer's Telegram, No.8356, Dec 2015}\\
\publication{The Astronomer's Telegram, No.8352, Dec 2015}\\
\publication{The Astronomer's Telegram, No.6158, May 2014}\\
\publication{The Astronomer's Telegram, No.6143, May 2014}\\
\publication{Central Bureau Electronic Telegrams, No. 3549, Jun 2013}\\
\publication{The Astronomer's Telegram, No.5110, Jun 2013}\\
\publication{The Astronomer's Telegram, No.5102, Jun 2013}\\
\publication{American Astronomical Society, AAS Meeting \#229, id.414.02, Jan 2017}\\
\publication{American Astronomical Society, AAS Meeting \#225, id.103.02, Jan 2015}\\
